\begin{thebibliography}{99}

  % 1
  \bibitem{angluin-ml1988}
  Angluin, D.:
  Queries and Concept Learning,
  Matching Learning, Vol.2, No.4, pp.319--342 (1988).

  % 2
  \bibitem{angluin-jcss1980}
  Angluin, D.:
  Finding patterns common to a set of strings,
  Journal of Computer and System Sciences, Vol.21, No.1, pp.46-62 (1980).

  % 3
  \bibitem{angluin-ic1987}
  Angluin, D.:
  Learning Regular Sets from Queries and Counterexamples,
  Information and Computation, Vol.75, No.2, pp.87-106 (1987).

  \bibitem{amoth-ml2001}
  Amoth, T.R., Cull, P., Tadepalli, P.:
  On Exact Learning of Unordered Tree Patterns,
  Machine Learning, Vol.44, pp211-243 (2001).

  %\bibitem{greenlaw-parallel1995}
  %Greenlaw, R., Hoover, H.J., and Ruzzo, W.L.:
  %Limits to Parallel Computation: P-Completeness Theory, 
  %Oxford University Press (1995).

  \bibitem{higashiyama-hinokuni2024}
  東山 的生, 内田 智之, 正代 隆義, 松本 哲志:
  順序項木パターンに対する学習済GCNをオラクルとした質問学習アルゴリズムのランダム化による精度向上,
  情報処理学会九州支部火の国情報シンポジウム講演論文集, B6-1, pp.1--6 (2024).

  \bibitem{pyg-gcnconv}
  Kipf, T. N. and Welling, M.: 
  Semi-Supervised Classification with Graph Convolutional Networks, 
  Proc. ICLR 2017, arXiv:1609.02907 (2017).

  \bibitem{matsumoto-ieice2020}
  Matsumoto, S., Uchida, T., Shoudai, T., Suzuki, Y., and Miyahara, T.:
  An Efficient Learning Algorithm for Regular Pattern Languages Using One Positive Example and a Linear Number of Membership Queries,
  IEICE Transactions on Information and Systems, Vol.E103-D, No.3, pp.526-539 (2020).

  %\bibitem{miyano-parallel1993}
  %宮野 悟:
  %並列アルゴリズム,
  %近代科学社 (1993).

  \bibitem{miyano-ngc2000}
  Miyano,~S., Shinohara,~A. and Shinohara,~T.:
  Polynomial-time Learning of Elementary Formal Systems,
  New Generation Computing, Vol.18, pp.217--242 (2000).

  \bibitem{pyg-graphconv}
  Morris, C. et al.: 
  Weisfeiler and Leman Go Neural: Higher-Order Graph Neural Networks, 
  Proc. AAAI Conference on Artificial Intelligence, 
  Vol.33, No.1, pp.4602-4609 (2019). 

  \bibitem{nii-nakano_uno2003}
  Nakano, S. and Uno, T.:
  Efficient generation of rooted trees,
  National Institute for Informatics (Japan),
  Tech. Rep. NII-2003-005E 8,
  pp.4--63, (2003).

  \bibitem{cs-nakano_uno2004}
  Nakano, S. and Uno, T.:
  Constant Time Generation of Trees with Specified Diameter, Graph-Theoretic Concepts in Computer Science (WG2004),
  LNCS 3353, pp.33-45 (2004).

  \bibitem{oda-ai2022}
  小田 直季, 内田 智之, 正代 隆義, 松本 哲志, 鈴木 祐介, 宮原 哲浩:
  順序木パターンの質問学習アルゴリズムによるグラフ畳み込みネットワークの予測根拠の可視化,
  2022年度人工知能学会全国大会(第36回), 2G4-GS-2-01 (2022).

  \bibitem{pyg-rgcnconv}
  Schlichtkrull, M. et al.: 
  Modeling Relational Data with Graph Convolutional Networks, 
  The Semantic Web, ESWC 2018, LNCS 10843, pp.593--607 (2018). 

  \bibitem{shoudai-ieice2018}
  Shoudai,~T., Miyahara,~T., Uchida,~T., Matsumoto,~S., and Suzuki,~Y.:
  An Efficient Pattern Matching Algorithm for Unordered Term Tree Patterns of Bounded Dimension,
  IEICE Trans. Fundamentals, Vol.E101-A, No.9, pp.1344--1354 (2018).

  \bibitem{suzuki-tcs2006}
  Suzuki, Y., Shoudai, T., Uchida, T., and Miyahara, T.:
  Ordered term tree languages which are polynomial time inductively inferable from positive data,
  Theoretical Computer Science, Vol.350, pp.63-90 (2006).

  \bibitem{uchida2014}
  Uchida, T., Matsumoto, S., Okada, R., Shoudai, T., Suzuki, Y., and Miyahara, T.:
  Exact Learning of Finite Unions of Graph Patterns from Queries,
  Journal of Information Processing, Vol.22, No.1, pp.1--8 (2014).

  \bibitem{uchida-ieice2019}
  Uchida, T., Matsumoto, S., Shoudai, T., Suzuki, Y., and Miyahara, T.:
  Exact Learning of Primitive Formal Systems Defining Labeled Ordered Tree Languages via Queries,
  IEICE Transactions on Information and Systems, Vol.E102-D, No.3, pp.470-482 (2019).

  %\bibitem{zaitsu}
  %財津 恭太:
  %順序項木パターンに対するNCマッチングアルゴリズム,
  %平成14年度九州大学大学院システム情報科学府修士論文 (2003).


\end{thebibliography}

% ファイリングしている参考文献を載せる